Network Configuration Synthesis with Abstract Topologies

### 2016-11-12 paper/abstraction/paper.tex
minor edits

\textbf{Abstract---}
We develop techniques for automated reasoning about end-to-end properties of abstract network topologies. We develop a network synthesis tool, \sysname, to allow network operators to write a high-level routing policy over an abstraction of their network topology. From such a specification, \sysname synthesizes a collection of router configurations running the distributed Border Gateway Protocol (BGP) that are guaranteed to implement the centralized routing policy for any concrete instantiation of the abstract topology, and for any combination of network failures in the resulting concrete topology.
%
Additionally, properties proven by \sysname over the abstract topology, such as reachability between a source and destination under k-failures, are also guaranteed to hold under any concrete instantiation of the abstract topology.
%
Something something, expandable/incremental networks. Something something scales compilation to large networks. Something something, templates easier to understand.
%These strong guarantees allow operators to reason about the routing behavior of their network at a high-level abstraction, while also generating an efficient low-level implementation.
%
%In addition, operators are able to safely change or expand their network in any way, so long as the new resulting topology also respects the abstraction.
%
We test \sysname out on ... blah blah blah

@@

%\vspace{0.1in}
%\noindent
%\textbf{CCS Concepts}\\
%$\bullet$ Networks $\rightarrow$ {\em Network control algorithms; Network reliability; Network management;}
%$\bullet$ Software and its engineering $\rightarrow$ {\em Automated static analysis; Domain specific languages}

%\vspace{0.1in}
%\noindent
%\textbf{Keywords}\\
%Propane; Domain-specific Language; BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems

@@

% Hence, one approach to improving network
% reliability is to develop better languages for network configuration.
% Such languages should be defined at a higher level of abstraction than
% existing configuration languages and provide support built-in support for
% verification of important properties, thereby avoiding entire classes
% of configuration errors automatically.

@@

Computer networks run many critical services, and every second of downtime is
costly at best and dangerous at worst.  Keeping these complex systems up and running 24/7 is an enormous challenge~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study}.
%
While hardware faults, rodents, power failures and natural disasters all pose problems, studies have consistently shown that human error in network configuration is one of the most error-prone task and the leading cause of network outages~\cite{juniper-study,xx}.

@@

We present \sysname, a system to generate provably-correct role templates. It allows operators to input \emph{abstract network topologies} in terms of roles and their connectivity. For instance, they may specify roles for ``top-of-rack'' and ``aggregation" routers and specify that every top-of-rack router connects to at least two aggregation routers (to tolerate the failure of a link to an aggregation router). Other inputs to \sysname include the routing policy of the network and its fault-tolerance requirements (e.g., the number of link failures to tolerate). For routing policy, we borrow notation from Propane~\cite{propane},  which specifies traffic paths at a high-level of abstraction. But while Propane policies
refer concrete devices, \sysname policies refer to abstract roles.

>>>>

\textbf{Abstract---}
We develop techniques for automated reasoning about end-to-end properties of
abstract network topologies, and embody them in a network synthesis tool called
\sysname. \sysname allows network operators to write a high-level routing policy
over an abstraction of their network topology. From such a specification,
\sysname synthesizes a collection of router configurations running the
distributed Border Gateway Protocol (BGP) that are guaranteed to implement the
centralized routing policy for any concrete instantiation of the abstract
topology, and for any combination of network failures in the resulting concrete
topology.
%
Additionally, properties proven by \sysname over the abstract topology, such as
reachability between a source and destination under k-failures, are also
guaranteed to hold under any concrete instantiation of the abstract topology.
%
Something something, expandable/incremental networks. Something something scales
compilation to large networks. Something something, templates easier to
understand.
%These strong guarantees allow operators to reason about the routing behavior of
%their network at a high-level abstraction, while also generating an efficient
%low-level implementation.
%
%In addition, operators are able to safely change or expand their network in any
%way, so long as the new resulting topology also respects the abstraction.
%
We test \sysname out on ... blah blah blah

@@

%\vspace{0.1in} \noindent \textbf{CCS Concepts}\\ $\bullet$ Networks
%$\rightarrow$ {\em Network control algorithms; Network reliability; Network
%management;} $\bullet$ Software and its engineering $\rightarrow$ {\em
%Automated static analysis; Domain specific languages}

%\vspace{0.1in} \noindent \textbf{Keywords}\\ Propane; Domain-specific Language;
%BGP; Synthesis; Compilation; Fault Tolerance; Distributed Systems

@@

% Hence, one approach to improving network reliability is to develop better
% languages for network configuration.  Such languages should be defined at a
% higher level of abstraction than existing configuration languages and provide
% support built-in support for verification of important properties, thereby
% avoiding entire classes of configuration errors automatically.

@@

Computer networks run many critical services, and every second of downtime is
costly at best and dangerous at worst.  Keeping these complex systems up and
running 24/7 is an enormous
challenge~\cite{mahajan+:bgp-misconfiguration,feamster+:rcc,batfish,dc-failure-study}.
%
While hardware faults, backhoes, power failures and natural disasters all pose
problems, studies have consistently shown that human error in network
configuration is one of the leading cause of network
outages~\cite{juniper-study,xx}.

@@

We present \sysname, a system to generate provably-correct role templates. It
allows operators to input \emph{abstract network topologies} in terms of roles
and their connectivity. For instance, they may specify roles for ``top-of-rack''
and ``aggregation" routers and specify that every top-of-rack router connects to
at least two aggregation routers (to tolerate the failure of a link to an
aggregation router). Other inputs to \sysname include the routing policy of the
network and its fault-tolerance requirements (e.g., the number of link failures
to tolerate). For routing policy, we borrow notation from
Propane~\cite{propane},  which specifies traffic paths at a high-level of
abstraction. But while Propane policies refer to concrete devices, \sysname
policies refer to abstract roles.
